This is a title

### 2024-05-28 paper/sections/01-intro.tex
Add kaggle information to the introduction

\begin{figure}
    \begin{center}
        \input{figs/model-diagram.tex}
        \caption{This diagram is just here temporarily and will be in a more relevant section when complete}
    \end{center}
\end{figure}

>>>>

% mention that the research is from a kaggle competition
The research was conducted as part of the GeoLifeCLEF 2024 competition on Kaggle \cite{geolifeclef-2024}, which is a part of the LifeCLEF initiative. The competition aims to develop models for predicting plant species in a specific location and time using various environmental factors as predictors.
